%-----------------------------------------------------------------------------------------------------------------------------------------------%
%   CV - Improved Clean Professional Layout
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%   FONT (optional - uncomment for XeLaTeX)
%----------------------------------------------------------------------------------------
\usepackage{fontspec}
\setmainfont{Cambria}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.90]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{fontawesome5}
\usepackage[unicode]{hyperref}

% Hyperlink color
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks, breaklinks, urlcolor=linkcolour, linkcolor=linkcolour}

%----------------------------------------------------------------------------------------
%   SECTION STYLE
%----------------------------------------------------------------------------------------
\titleformat{\section}
  {\Large\bfseries\scshape}
  {}
  {0pt}
  {}
  [\vspace{-4pt}\titlerule]

\titlespacing{\section}{0pt}{12pt}{6pt}

%----------------------------------------------------------------------------------------
%   ITEM SPACING
%----------------------------------------------------------------------------------------
\setlist[itemize]{nosep, topsep=2pt, itemsep=3pt, leftmargin=1em}

%----------------------------------------------------------------------------------------
%   DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{AHMED FARAZ}}\\[2pt]  % Name
    {\large Software Engineer | Tech Trainer}\\[6pt]  % Headline
    \href{mailto:ahmedfaraz.contact@gmail.com}{ahmedfaraz.contact@gmail.com}
    \quad | \quad
    \href{tel:+923413901064}{+92 (341) 3901064}
    \quad | \quad
    \href{https://linkedin.com/in/aahmedfaraz}{linkedin.com/in/aahmedfaraz}
    \quad | \quad
    \href{https://github.com/aahmedfaraz}{github.com/aahmedfaraz}
\end{center}

%----------------------------------------------------------------------------------------
%   HONORS & ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Honors \& Achievements}
\begin{itemize}
    \item \href{https://drive.google.com/file/d/1uHFju1PVdf3HQKPWlZkGIML0tiujyYCi/view?usp=sharing}{Academic IELTS -- \textbf{7.5} (\textbf{CEFR: C1})} (Speaking \textbf{7.5}, Reading \textbf{8.5}, Listening \textbf{7.5}, Writing \textbf{6.5})
    \item \textbf{Secured 1st place} in \href{https://certificates.cs50.io/5ed8854f-112a-4bbb-bb85-108d92f3233b.pdf?size=letter}{Harvard's CS50x Puzzle Day 2025} by solving 9/9 problems.
\end{itemize}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Bachelor of Software Engineering (BSE)} & \textbf{2019 -- 2023} \\
Bahria University Karachi Campus & CGPA: \textbf{3.09}/4.0 \\
\end{tabularx}
\textbf{Coursework:} DSA, OOP, DBMS, Operating Systems, Probability \& Statistics, AI, Web Engineering, Computer Networks.

%----------------------------------------------------------------------------------------
%   INTERNATIONAL EVENTS & COMPETITIONS
%----------------------------------------------------------------------------------------
\section{International Events \& Competitions}
\begin{itemize}
    \item Qualified for \href{https://www.facebook.com/codingcompetitions/hacker-cup/2025/certificate/1142880171157242}{Round 1 of the Meta Hacker Cup 2025}.
    \item Qualified in the \href{https://icscompetition.org/c/Certificate-QR-2025-FFB74B80AA6-94ee910f6d161e712e70cca319d93761.pdf}{International Computer Science Competition (ICSC) 2025}.
    \item Participated in the \href{https://www.linkedin.com/posts/aahmedfaraz_learning-growthmindset-failuretosuccess-activity-7399509376488615936-rtZd?utm_source=share&utm_medium=member_desktop&rcm=ACoAADdJH-cBzPnm9JIV3RhrpK_TvX28bFX_rEY}{CALICO Informatics Competition (UC Berkeley), 2025}.
    \item Participated in the \href{https://lablab.ai/u/@ahmed_faraz702/cmi68u64000fg6z0sucqab7az}{AI Genesis Hackathon} (Google AI Studio, AppliedAI, Qdrant)
    \hfill \textit{\href{https://www.linkedin.com/posts/aahmedfaraz_hackathon-ai-electron-activity-7397141415165726720-tlQq?utm_source=share&utm_medium=member_desktop&rcm=ACoAADdJH-cBzPnm9JIV3RhrpK_TvX28bFX_rEY}{\faLink \underline{View Demo}}}
    \item Participated in the \href{https://lablab.ai/u/@ahmed_faraz702/cmit0n778002nda0s8fmq2rur}{Agentic AI Hackathon with IBM watsonx Orchestrate}.
    \hfill \textit{\href{https://www.linkedin.com/posts/aahmedfaraz_ibm-watsonx-agenticai-activity-7403253209386979328-dxEk?utm_source=share&utm_medium=member_desktop&rcm=ACoAADdJH-cBzPnm9JIV3RhrpK_TvX28bFX_rEY}{\faLink \underline{View Demo}}}
    \item Participated in Hack the Future Hackathon organized by Qubic.
    \hfill \textit{\href{https://www.linkedin.com/posts/aahmedfaraz_qubic-lablabai-blockchain-activity-7403681197790408704-Aq7n?utm_source=share&utm_medium=member_desktop&rcm=ACoAADdJH-cBzPnm9JIV3RhrpK_TvX28bFX_rEY}{\faLink \underline{View Details}}}
\end{itemize}

%----------------------------------------------------------------------------------------
%   TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------
\section*{Teaching Experience}
\vspace{2pt}

% Techbeez
\textbf{Founder \& Instructor} \hfill \textbf{Remote (1 year)} \\
\textbf{Techbeez Education – Karachi, Pakistan} \hfill Jul 2022 -- Jul 2023
\begin{itemize}
    \item Designed and taught the \textbf{Techbeez FWDP (Frontend Web Developer Program)}.
    \item Taught web fundamentals including HTML, CSS, JavaScript, Git/GitHub, and basic web protocols.
    \item Led hands-on projects using JavaScript and modern frontend frameworks such as React and Redux.
    \item Mentored \textbf{60+ students} to build portfolio-ready web applications. \hfill \textit{\href{https://drive.google.com/drive/folders/1F0KtN6dNdHOWCGQpFw13_GGI_SMug7X_?usp=sharing}{\faLink \underline{View Course Content}}}
\end{itemize}

% Axiom
\textbf{Lead Technical Instructor} \hfill \textbf{Part-time (1.5 years)} \\
\textbf{Axiom Education – Karachi, Pakistan} \hfill Oct 2021 -- Feb 2023
\begin{itemize}
    \item Progressed from Assistant Instructor to \textbf{Lead Instructor}.
    \item Delivered project-based training for \textbf{full-stack web development} using MERN.
    \item MERN Stack = \textbf{MongoDB, Express.js, React, and Node.js}.
    % \item Designed 10 JavaScript projects emphasizing core language concepts and DOM manipulation.
    \item Conducted live coding sessions and supervised end-to-end web application projects.
    \item Trained and mentored \textbf{300+ students}.
\end{itemize}

%----------------------------------------------------------------------------------------
%   VOLUNTEER WORK
%----------------------------------------------------------------------------------------
\section*{Volunteer Work}

\textbf{Trainer and Moderator} \hfill \textbf{Remote (Aug 2025 -- Present)} \\
\textbf{iCodeGuru – Santa Clara, California}
\begin{itemize}
    \item Conducted a free \textbf{IELTS Speaking Course} for under-privileged students, offering structured lessons and practice sessions. \hfill \textit{\href{https://youtube.com/playlist?list=PLBXi_ryTbHgrKS_TljSEjycW0LwMTWfD3&si=ndIs0IgzNoVFCsPA}{\faLink \underline{View YouTube Playlist}}}
\end{itemize}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Languages} & JavaScript, TypeScript, Python \\
\textbf{IaC} & AWS CDK (serverless architectures) \\
\textbf{AWS Services} & IAM, Lambda, AppSync, Cognito, S3, Pinpoint, \textbf{and 20+ more} \\
\textbf{Frontend} & React, Next.js \\
\textbf{Backend} & Node.js, AWS serverless stack \\
\textbf{SQL Databases} & Aurora, RDS (MySQL, PostgreSQL), Redshift \\
\textbf{NoSQL} & DynamoDB, MongoDB \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section*{Work Experience}
\vspace{2pt}

% Road2Crypto
\textbf{AWS Full Stack Developer} \hfill \textbf{Remote (2+ years)} \\
\textbf{Road2Crypto – Miami, Florida, USA} \hfill Mar 2023 -- Aug 2025
\begin{itemize}
    \item Developed and launched \textbf{Road2Crypto}, a multi-wallet, cross-chain crypto tracking platform.
    \item Scaled backend architecture using AWS services, ensuring high availability, security, and performance.
    \item Delivered features across frontend, backend, and \textbf{AWS CDK} infrastructure in a serverless environment.
    \item Integrated \textbf{Stripe} for secure subscription and payment handling, enabling premium product features.
    \item Collaborated remotely with an \textbf{international engineering team} to deliver core product functionality.
\end{itemize}

% Panacloud
\textbf{AWS Modern Apps Full Stack Developer} \hfill \textbf{On-site (1.5 years)} \\
\textbf{Panacloud – Karachi, Pakistan} \hfill Oct 2021 -- Feb 2023
\begin{itemize}
    \item Progressed from cloud development intern to Full Stack Developer. 
    \item Contributed to cloud-native \textbf{eCommerce and EdTech platforms}.
    \item Led feature development across frontend and backend using Infrastructure as Code (AWS CDK).
    \item Built backend systems with \textbf{relational databases (Aurora)} and \textbf{NoSQL databases (DynamoDB)}.
    \item Used \textbf{AWS CDK} to manage infrastructure and deployments.
\end{itemize}

%----------------------------------------------------------------------------------------
%   HIGHLIGHTED PROJECTS
%----------------------------------------------------------------------------------------
\section*{Highlighted Projects}
\vspace{2pt} % small space after section title

% Road2Crypto
\vspace{4pt} % space before project
\textbf{Road2Crypto – Web Application}
\begin{itemize}
    \item Built and launched \textbf{Road2Crypto}, a platform to track multiple crypto wallets. 
    \hfill \textit{\href{https://road2crypto.com/assets?address=0x5d1d84d7d03016c505720e05f689cc49d77ebcb2}{\faLink \underline{Visit Platform}}}
    \item Frontend developed with \textbf{Next.js} for a fast and responsive interface.
    \item Backend on \textbf{AWS serverless architecture} for scalability and security.
    \item Integrated \textbf{CoinGecko API} for real-time crypto data.
    \item Added \textbf{Stripe} for secure payments and subscriptions.
    \item Worked remotely with an \textbf{international team} to deliver core features.
\end{itemize}

% AirMouse
\vspace{6pt} % extra space between projects
\textbf{AirMouse – AI Desktop App}
\begin{itemize}
    \item Developed an AI app to control the cursor with hand gestures. 
    \hfill \textit{\href{https://www.linkedin.com/posts/aahmedfaraz_hackathon-ai-electron-activity-7397141415165726720-tlQq?utm_source=share&utm_medium=member_desktop&rcm=ACoAADdJH-cBzPnm9JIV3RhrpK_TvX28bFX_rEY}{\faLink \underline{Watch Demo}}}
    \item Used \textbf{MediaPipe Hands} for real-time hand tracking.
    \item Built with \textbf{Electron} and \textbf{React}, code in \textbf{TypeScript}.
    \item Controlled OS-level mouse movements using \textbf{@nut-tree-fork/nut-js}.
    \item Created during \textbf{AI Genesis Hackathon} by lablab.ai.
    \item Download the app \hfill \textit{\href{https://github.com/aahmedfaraz/air-mouse/releases/tag/v1.0.0}{\faLink \underline{Get App}}}
\end{itemize}

%----------------------------------------------------------------------------------------
%   REFERENCES
%----------------------------------------------------------------------------------------
\section*{References}

\vspace{2pt}
\textbf{Arturo Fernandez — CEO, Road2Crypto} \hfill \href{https://www.linkedin.com/in/afern247}{linkedin.com/in/afern247}
\begin{itemize}[nosep, topsep=0pt, partopsep=0pt, leftmargin=1em]
    \item Email: \href{mailto:afern@road2crypto.com}{afern@road2crypto.com} 
    \item Phone: +1 786 536 0020
    \item Location: Miami, Florida, USA
\end{itemize}

\vspace{2pt}
\textbf{Adil Altaf — CTO CyberNut (Ex-CIO Panacloud)} \hfill \href{https://www.linkedin.com/in/adilaltaf/}{linkedin.com/in/adilaltaf}
\begin{itemize}[nosep, topsep=0pt, partopsep=0pt, leftmargin=1em]
    \item Email: \href{mailto:adil@outlook.com}{adil@outlook.com}
    \item Phone: +1 408 883 0340
    \item Location: Reston, Virginia, USA
\end{itemize}

\vspace{2pt}
\textbf{Dr. Zafar Shahid — Technical Lead / Staff Engineer @ Meta} \hfill \href{https://www.linkedin.com/in/zafarshahid/}{linkedin.com/in/zafarshahid}
\begin{itemize}[nosep, topsep=0pt, partopsep=0pt, leftmargin=1em]
    \item Email: \href{mailto:zafar.shahid@acm.org}{zafar.shahid@acm.org}
    \item Phone: +1 512 239 8008
    \item Location: Santa Clara, California, USA
\end{itemize}

\vspace{2pt}
\textbf{Dr. Rizwan Ghaffar — Principal Engineer @ Broadcom Inc.} \hfill \href{https://www.linkedin.com/in/rizwan-ghaffar/}{linkedin.com/in/rizwanghaffar}
\begin{itemize}[nosep, topsep=0pt, partopsep=0pt, leftmargin=1em]
    \item Email: \href{mailto:rizwanghaffar24@gmail.com}{rizwanghaffar24@gmail.com}
    \item Phone: +1 858 216 5405
    \item Location: San Jose, California, USA
\end{itemize}

% %----------------------------------------------------------------------------------------
% %   FOOTER
% %----------------------------------------------------------------------------------------
% \vfill
% \center{\footnotesize Last updated: \today}

\end{document}
